Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-20 paper/paper.qmd
summary stats and plots updated based on new data

library(tidyverse)
library(janitor)
library(here)
library(lubridate)
library(arrow)
library(dplyr)
library(knitr)
library(performance)
library(kableExtra)
library(performance)
library(ggpubr)

@@

```{r}
#| label: tbl-summary-1
#| tbl-cap: "Summary Statistics for Quantitative Variables"
#| echo: false
#| warning: false
#| message: false
library(knitr)
library(stringr)

# Calculate Means and SDs by Time for GameScore
game_means <- tapply(clean_data$GameScore, clean_data$Time, mean, na.rm = TRUE)
game_sds   <- tapply(clean_data$GameScore, clean_data$Time, sd, na.rm = TRUE)

# Calculate Means and SDs by Time for CardScore
cards_means <- tapply(clean_data$CardScore, clean_data$Time, mean, na.rm = TRUE)
cards_sds   <- tapply(clean_data$CardScore, clean_data$Time, sd, na.rm = TRUE)

# Combine into a data frame for kable
summary_table <- data.frame(
  Time = names(game_means),
  Game_Mean = round(game_means, 2),
  Game_SD   = round(game_sds, 2),
  Cards_Mean = round(cards_means, 2),
  Cards_SD   = round(cards_sds, 2)
)

summary_table$Time <- str_to_title(summary_table$Time)

# Display table with no row names
kable(summary_table, booktabs = TRUE, row.names = FALSE)

@@

```{r}
library(dplyr)
library(knitr)

>>>>

library(tidyverse)
library(janitor)
library(here)
library(lubridate)
library(arrow)
library(dplyr)
library(knitr)
library(performance)
library(stringr)
library(kableExtra)
library(performance)
library(ggpubr)

@@

```{r}
#| label: tbl-summary-1
#| tbl-cap: "Summary Statistics for Quantitative Variables"
#| echo: false
#| warning: false
#| message: false

# Compute statistics for Memory Game Score
mean_game <- mean(clean_data$memory_game_score, na.rm = TRUE)
median_game <- median(clean_data$memory_game_score, na.rm = TRUE)
sd_game <- sd(clean_data$memory_game_score, na.rm = TRUE)
iqr_game <- IQR(clean_data$memory_game_score, na.rm = TRUE)

# Compute statistics for Memory Cards Score
mean_cards <- mean(clean_data$memory_cards_score, na.rm = TRUE)
median_cards <- median(clean_data$memory_cards_score, na.rm = TRUE)
sd_cards <- sd(clean_data$memory_cards_score, na.rm = TRUE)
iqr_cards <- IQR(clean_data$memory_cards_score, na.rm = TRUE)

# Combine into a summary table
summary_table <- data.frame(
  Statistic = c("Mean", "Median", "SD", "IQR"),
  `Memory Game Score` = c(mean_game, median_game, sd_game, iqr_game),
  `Memory Cards Score` = c(mean_cards, median_cards, sd_cards, iqr_cards)
)

# Display the table

kable(summary_table, format = "latex", booktabs = TRUE)

@@

```{r}
